---
title: "Jason Gao | Personal Website"
output: 
  html_document:
    toc: true
    toc_float: true
---
# Welcome to Jason's Personal Website

This website showcases my projects for **P8105: Data Science I (Homework 4)** and other topics that reflect my personal interests and work.  

* You can learn more [**about me**](about.html) in the **About** section.  
* If you’d like to connect or explore my other work, feel free to visit my [**GitHub page**](https://github.com/jason-0409-g) — just click the GitHub logo in the top-left corner.  
* 📧 You can also reach me directly via email at [jiangao0409@foxmail.com](mailto:jiangao0409@foxmail.com) or click the mail logo in the top-left corner.



# Now, I will show the result of the Homework 4 about Q_2

Loading the package and datasets
```{r,setup,include=FALSE}
library(tidyverse)
library(plotly)
library(flexdashboard)
library(p8105.datasets)

data("instacart")
set.seed(123)

# Randomly sample 5000 rows to improve rendering speed
instacart_samp <- instacart |> sample_n(5000)
```


# Scatter Plot: Hour vs Add-to-Cart (Interactive scatter plot)


```{r}
p_scatter <- instacart_samp |>
  plot_ly(
    x = ~order_hour_of_day, 
    y = ~add_to_cart_order,
    type = "scatter", 
    mode = "markers",
    color = ~reordered,
    colors = c("#00AFBB", "#E7B800"),
    alpha = 0.5,
    text = ~paste("Product:", product_name,
                  "<br>Order ID:", order_id)
  ) |>
  layout(
    title = "Relationship between shopping hour and add-to-cart order",
    xaxis = list(title = "Hour of day"),
    yaxis = list(title = "Add-to-cart order")
  )

p_scatter
```



# Box Plot: Distribution of Add-to-Cart Order by Department

```{r}
p_box <- instacart_samp |>
  mutate(department = fct_lump(department, 10)) |>
  plot_ly(
    y = ~add_to_cart_order,
    color = ~department,
    type = "box",
    colors = "Set3"
  ) |>
  layout(
    title = "Add-to-cart order by department",
    yaxis = list(title = "Add-to-cart order")
  )

p_box
```




# Bar Chart: Most Frequent Aisles Ordered From

```{r, warning=FALSE}
p_bar <- instacart_samp |>
  count(aisle, sort = TRUE) |>
  slice_head(n = 15) |>
  mutate(aisle = fct_reorder(aisle, n)) |>
  plot_ly(
    x = ~aisle, y = ~n,
    type = "bar",
    color = ~aisle,
    colors = "Blues"
  ) |>
  layout(
    title = "Top 15 Aisles by Order Count",
    xaxis = list(title = ""),
    yaxis = list(title = "Number of Orders")
  )

p_bar
```




